\LaTeX\ Author Guidelines for ICCV Proceedings

### 2020-11-06 chapters/supplementary.tex
Small changes to supplementaries

\subsection{Neuron segmentation and compared methods}\label{sec:cremi_details}
\paragraph{Training details} The data from the CREMI challenge is highly anisotropic and contains artifacts like missing sections, staining precipitations and support film folds. 
To alleviate difficulties stemming from misalignment, we use a version of the data that was elastically realigned by the challenge organizers with the method of \cite{saalfeld2012elastic}.
We train a 3D U-Net \cite{ronneberger2015u, cciccek20163d} using the same architecture as \cite{funke2018large} and predict long-and-short range affinities 
as described in \cite{lee2017superhuman}. In addition to the standard data augmentation techniques of random rotations, random flips and  elastic deformations, we simulate data artifacts.
In more detail, we randomly zero-out slices, decrease the contrast of slices, simulate tears, introduce alignment jitter and paste artifacts extracted from the training data. Both \cite{funke2018large} and \cite{lee2017superhuman} have shown
that these kinds of augmentations can help to alleviate issues caused by EM-imaging artifacts.
We use L2 loss and Adam optimizer to train the network. The model was trained on all the three samples with available ground truth labels.

@@

The experiments summarized in Fig. \ref{fig:noise_plots} were performed in the following way: for each value $\mathcal{K}$, 30 random noise samples were drawn, from which median and percentiles statistics were computed for each different linkage criteria. For each sample, we randomly selected some of the long-range predictions from the CNN and added them to pixel grid-graph.
\begin{figure}[t]
\centering
        \includegraphics[width=\textwidth,trim=0.0in -0.in -0.0in -0.4in,clip]{figs/noisy_affs_comparison.pdf}
    \caption{CNN predictions on a slice of the CREMI neuron segmentation challenge with and without additional noise. (\textbf{a}) Raw data (\textbf{b}) Original CNN predictions $F(x)$, where blue pixels represent boundary evidence (\textbf{c}) Under-clustering biased version $\tilde{F}_{+}(x;\mathcal{K})$ of the predictions defined in Eq. \ref{eq:noise_biased_predictions} with $\mathcal{K}=8$ (\textbf{d}) Over-clustering biased version $\tilde{F}_{-}(x;\mathcal{K})$. Long-range predictions are not shown.
    }
    \label{fig:noisy_affs}
\end{figure}
\begin{table}
    \centering
    % \small
    \vspace*{0.6em}
        \begin{tabular}{l|c|c}
          \algname{} linkage & AP  & Bias $\beta$ \\ \midrule
          Average & 34.3 & 0.35 \\
          Average + CLC & 33.9 & 0.25\\
          Max + CLC & 32.5 & 0.50 \\
          Abs Max & 32.1 & 0.45\\
          Sum + CLC & 31.9 & 0.55 \\
          Sum & 31.3 & 0.55 \\
          Max & 24.3 & 0.85 \\
          Min & 0.00 & 0.50 \\
          Min + CLC & 0.00 & 0.50 \\
        \end{tabular}
    \vspace*{2em}
    \caption{Average Precision (AP) scores achieved by different versions of \algname{} and chosen bias parameters $\beta$ on the cityscapes validation set. A bias value $\beta=0$ returns one single cluster. CLC stands for cannot-link constraints}
    \label{tab:extended_results_cityscapes_val}
\end{table}

>>>>

\subsection{Neuron segmentation and compared methods}\label{sec:cremi_details}
\paragraph{Training details} The data from the CREMI challenge is highly anisotropic and contains artifacts like missing sections, staining precipitations and support film folds. 
To alleviate difficulties stemming from misalignment, we use a version of the data that was elastically realigned by the challenge organizers with the method of \cite{saalfeld2012elastic}.
We train a 3D U-Net \cite{ronneberger2015u,cciccek20163d} using the same architecture as \cite{funke2018large} and predict long-and-short range affinities 
as described in \cite{lee2017superhuman}. In addition to the standard data augmentation techniques of random rotations, random flips and  elastic deformations, we simulate data artifacts.
In more detail, we randomly zero-out slices, decrease the contrast of slices, simulate tears, introduce alignment jitter and paste artifacts extracted from the training data. Both \cite{funke2018large} and \cite{lee2017superhuman} have shown
that these kinds of augmentations can help to alleviate issues caused by EM-imaging artifacts.
We use L2 loss and Adam optimizer to train the network. The model was trained on all the three samples with available ground truth labels.

@@

The experiments summarized in Fig. \ref{fig:noise_plots} were performed in the following way: for each value $\mathcal{K}$, 30 random noise samples were drawn, from which median and percentiles statistics were computed for each different linkage criteria. For each sample, we randomly selected some of the long-range predictions from the CNN and added them to pixel grid-graph.
\begin{figure}[t]
\centering
        \includegraphics[width=\textwidth,trim=0.0in -0.in -0.0in -0.4in,clip]{figs/noisy_affs_comparison.pdf}
    \caption{CNN predictions on a slice of the CREMI neuron segmentation challenge with and without additional noise. (\textbf{a}) Raw data (\textbf{b}) Original CNN predictions $F(x)$, where blue pixels represent boundary evidence (\textbf{c}) Under-clustering biased version $\tilde{F}_{+}(x;\mathcal{K})$ of the predictions defined in Eq. \ref{eq:noise_biased_predictions} with $\mathcal{K}=8$ (\textbf{d}) Over-clustering biased version $\tilde{F}_{-}(x;\mathcal{K})$. Long-range predictions are not shown.
    }
    \label{fig:noisy_affs}
\end{figure}
\begin{table}
    \centering
    % \small
    \vspace*{0.6em}
        \begin{tabular}{l M{7em} M{7em}}
          \algname{} linkage & AP  & Bias $\beta$ \\ \midrule
          Average & 34.3 & 0.35 \\
          Average + CLC & 33.9 & 0.25\\
          Max + CLC & 32.5 & 0.50 \\
          Abs Max & 32.1 & 0.45\\
          Sum + CLC & 31.9 & 0.55 \\
          Sum & 31.3 & 0.55 \\
          Max & 24.3 & 0.85 \\
          Min & 0.00 & 0.50 \\
          Min + CLC & 0.00 & 0.50 \\
        \end{tabular}
    \vspace*{2em}
    \caption{Average Precision (AP) scores achieved by different versions of \algname{} and chosen bias parameters $\beta$ on the cityscapes validation set. A bias value $\beta=0$ returns one single cluster. CLC stands for cannot-link constraints.}
    \label{tab:extended_results_cityscapes_val}
\end{table}
